Star-galaxy Classification Using Deep Convolutional Neural Networks

### 2016-08-11 paper/main.tex
[issue 2.17] why tpc, not sklearn rf?

To compare the performance of ConvNets with
machine learning algorithms that use standard photometric features,
we use a machine learning framework called
Trees for Probabilistic Classifications (TPC).
TPC is a parallel, supervised machine learning algorithm
that uses prediction trees and random forest 
techniques~\citep{breiman1984classification, breiman2001random}
to produce a star-galaxy classification.
\changed{
A complete description of TPC is beyond the scope of this paper, and
we refer the reader to
\cite{carrascokind2013tpz} and \cite{kim2015hybrid} for more details.
}

>>>>

To compare the performance of ConvNets with
machine learning algorithms that use standard photometric features,
we use a machine learning framework called
Trees for Probabilistic Classifications (TPC).
TPC is a parallel, supervised machine learning algorithm
that uses prediction trees and random forest 
techniques~\citep{breiman1984classification, breiman2001random}
to produce a star-galaxy classification.
\changed{
A complete description of TPC is beyond the scope of this paper, and
we refer the reader to
\cite{carrascokind2013tpz} and \cite{kim2015hybrid} for more details.
While other random forest implementations exist, we have chosen TPC, because
it is tailored specifically for astronomical use~\citep{carrascokind2013tpz};
it has been tested for astronomical use cases, including
photometric redshift estimation~\citep{sanchez2014photometric}
and star-galaxy classification~\citep{kim2015hybrid};
it adds an extra layer of randomness by perturbing the measured attributes by
their uncertainties;
and it uses parallelism to handle large data sets on distributed memory systems.
}
